---
title: "Data Science Homework 6"
author: "Thirsten Stockton"
date: "2022-12-03"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(modelr)

```

# Problem 1

**Code to bring in data**

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

***Plotting distribution of bootstapped r-sqaured estimates***
```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```


***95% confidence interval for r-squared estimate***

```{r}
rsq_bootstrap =
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) 

quantile(rsq_bootstrap$r.squared, c(0.025, 0.975))
```

The distribution of r-squared estimates shows a slight left skew and is rather narrow. The estimated 95% confidence interval is (0.8937494, 0.9274768), though due to the skewed nature of the data, this may not be the best estimate. 

***Plotting distribution of $\log(\beta_0 * \beta1)$***

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

***95% confidence interval for $\log(\beta_0 * \beta1)$ estimate***
```{r}

log_betas_bootstrap =
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) 


quantile(log_betas_bootstrap$log_b0b1, c(0.025, 0.975))
```

Similar to the r-squared plot, this plot shows a slight left skew. The 95% confidence inteval for this estimate is (1.962837, 2.059418), but like the first estimate, the 95% CI may not be reliable due to skewness.

